\begin{thebibliography}{9}
\small

% ------------------ EXAMPLE ------------------------------

\bibitem{JakasNazwa}
Autor, \emph{Tytuł}, Wydawnictwo, Rok wydania.

\bibitem{Internetowe}
Tytuł strony, \emph{Tytuł artykułu}, \emph{http://adres.strony} (dostęp:20.10.2023).

% ------------------ WSTEP   ------------------------------

% ------------------ ROZDZIAL 1 ------------------------------
\bibitem{Kleinberg}
Impossibility Theorem for Clustering
\emph{Theorem for Clustering}, \emph{https://www.cs.cornell.edu/home/kleinber/nips15.pdf}

\bibitem{Clustering}
A. K. Jain, R. C. Dubes, \emph{Algorithms for Clustering Data}, Prentice-Hall, Inc., 1988.

\bibitem{NLP}
Daniel Jurafsky, James H. Martin, 
\emph{Speech and Language Processing}, \emph{https://web.stanford.edu/~jurafsky/slp3/ed3book.pdf},
Stanford University., 2024.

\bibitem{Vectorization}
C. C. Aggarwal, C. Zhai (Eds.), \emph{Mining Text Data}, Springer, 2012.

\bibitem{DimensionReduction}
A. Y. Ng, M. I. Jordan, Y. Weiss, \emph{On Spectral Clustering: Analysis and an Algorithm}, Advances in Neural Information Processing Systems, 14, 2001.

% ------------------ ROZDZIAL 2 ------------------------------

\bibitem{YouTubeAPI}
YouTube Data API \emph{YouTube Data API}, \emph{https://developers.google.com/youtube/v3/docs?hl=pl}

\bibitem{nltk}
Steven Bird, Ewan Klein, Edward Loper, \emph{Natural Language Processing with Python}, O'Reilly Media, 2009.

\bibitem{scikit-learn}
F. Pedregosa et al., \emph{Scikit-learn: Machine Learning in Python}, Journal of Machine Learning Research, 12, pp. 2825-2830, 2011.

\bibitem{gensim}
Radim Řehůřek, Petr Sojka, \emph{Software Framework for Topic Modelling with Large Corpora}, In Proceedings of the LREC 2010 Workshop on New Challenges for NLP Frameworks, pp. 45-50, 2010.

\bibitem{tf-idf}
G. Salton, A. Wong, C. S. Yang, \emph{A Vector Space Model for Automatic Indexing}, Communications of the ACM, 18(11), pp. 613-620, 1975.

\bibitem{word2vec}
Tomas Mikolov, Kai Chen, Greg Corrado, Jeffrey Dean, \emph{Efficient Estimation of Word Representations in Vector Space}, arXiv preprint arXiv:1301.3781, 2013.

\bibitem{k-means}
J. MacQueen, \emph{Some Methods for Classification and Analysis of Multivariate Observations}, In Proceedings of the Fifth Berkeley Symposium on Mathematical Statistics and Probability (Vol. 1, No. 14, pp. 281-297), 1967.

\bibitem{dbscan}
M. Ester, H. P. Kriegel, J. Sander, X. Xu, \emph{A Density-Based Algorithm for Discovering Clusters in Large Spatial Databases with Noise}, In KDD (Vol. 96, No. 34, pp. 226-231), 1996.

\bibitem{t-sne}
L. van der Maaten, G. Hinton, \emph{Visualizing Data using t-SNE}, Journal of Machine Learning Research, 9(Nov), pp. 2579-2605, 2008.

% ------------------ ROZDZIAL 3 ------------------------------

\bibitem{PyQt}
Mark Summerfield, \emph{Rapid GUI Programming with Python and Qt}, Prentice Hall, 2007.

\bibitem{MatPlotLib}
John D. Hunter, \emph{Matplotlib: A 2D Graphics Environment}, Computing in Science And Engineering, 9(3), pp. 90-95, 2007.

\bibitem{mplcursor}
Matplotlib Development Team, \emph{mplcursors}, \emph{https://mplcursors.readthedocs.io/}, (доступ: 20.10.2023).

% ------------------ ROZDZIAL 4 ------------------------------

% ------------------ PODSUMOWANIE ------------------------------


\end{thebibliography}
